---
title: "mytilus_nucella"
author: "Tena Dhayalan"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: cosmo
    toc: yes
    toc_float:
      collapsed: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning=FALSE, 
                      message=FALSE)
```

### Loading libraries

```{r,echo=FALSE, message=FALSE}
library(dplyr)
library(broom)
library(purrr)
library(lubridate)
library(tidyverse)
library(nlstools)
library(here)
library(stringr)
library(lmerTest)
library(lme4)
library(knitr)
require(kableExtra)
library(tidyverse)
library(car)
library(patchwork)
library(seacarb)
options(knitr.table.format = "html")
```

### Load data

```{r,echo=FALSE, message=FALSE}
calc <- read_csv(here("Data", "TA", "NEC.csv")) # calcification 
tankpH <- read_csv(here("Data", "pH_temp", "ph_temp_final_cut.csv.")) # ph and temp data
respo <- read_csv(here("Data", "PR_2024", "PR_final_normalized_dry.csv")) # respo
Sample.Info <- read_csv(here("Data", "PR_2024", "Metadata.csv")) # respo metadata
mussel_initial <- read_csv(here("Data", "growth", "mytilus_initial.csv")) # initial mussel measurements
mussel_final <- read_csv(here("Data", "afdw", "mussel_afdw.csv")) # final mussel measurements
nucella_initial <- read_csv(here("Data", "growth", "nucella_initial.csv")) # initial nucella measurements
nucella_final <- read_csv(here("Data", "afdw", "nucella_afdw.csv")) # final nucella measurements
mortality <- read_csv(here("Data","mytilus_mortality.csv")) # mussel mortality
musselrespo_trimmed <- read_csv(here("Data", "PR_2024", "PR_final_normalized_dry_test.csv")) 
quadrat <- read_csv(here("Data", "field", "quadrat.csv"))
temp <- read.csv(here("Data","field","san_pedro_temp_buoy.csv")) #https://data.caloos.org/#metadata/103471/station/data
TA <- read.csv(here("Data","TA","background_TA","background_TA.csv"))
```

## carb data
```{r}
carb <- carb(8, var1 = TA$pH, var2 = TA$TA, S = TA$Salinity_lab, T = TA$TempInSitu, pHscale = "T")

carb <- carb %>%
  left_join(TA)

carb %>%
  ggplot(aes(x = tank, y = OmegaCalcite, group = tank)) +
  geom_boxplot()

write.csv(carb, here("Data/pH_temp/carb.csv"))
```


## Add tank data

```{r}
tankpHavg <- aggregate(cbind(pH,TempInSitu) ~ tank, data = tankpH, FUN = mean) # calculate avg pHs per tank

tankpH %>%
  ggplot(aes(x=expected_pH, y= pH, group = expected_pH, color = expected_pH))+
  geom_boxplot(width=0.1, outlier.alpha = 0.1)+
  scale_color_gradient(low = "palegreen2", high = "#0072B2")+
  theme_bw()+
  theme(strip.background = element_rect(fill = "white"),
        text = element_text(size = 16)) +
  theme(legend.position = "none") +
  labs(x = "Expected pH", y = "Average tank pH", color = "")

respo <-
  respo %>%
  left_join(tankpHavg, by = "tank") %>%
  mutate(temp_treatment = as.factor(temp_treatment))

tankpH %>%
  ggplot(aes(x=as.factor(expected_temp), y= TempInSitu, group = expected_temp, color = as.factor(expected_temp)))+
  geom_boxplot(width = 0.5, outlier.alpha = 0.1)+
  scale_color_manual(values = c("#0072B2", "#D55E00")) +
  theme_bw()+
  theme(strip.background = element_rect(fill = "white"),
        text = element_text(size = 16)) +
  theme(legend.position = "none") +
  labs(x = "Expected temperature", y = "Average tank temperature", color = "")
```

# field

```{r}
states<-map_data("state") #all state coordinates
ca_data <- states %>%
  filter(region == "california") #just filter out california

ggplot()+
  geom_polygon(data = ca_data,
               aes(x=long, y=lat, group = group), color = "black")+
  geom_point(aes(x = -118.319, y = 33.715), color= "blue", size = 5)+
  coord_map()+
  theme_void()
```
## field temp
```{r}
# calculate weekly averages
temp <- temp %>%
  mutate(date = as.Date(date, format="%m/%d/%Y")) # adjust date format

temp <- temp %>%
  group_by(week = floor_date(date, "week")) %>%  # groups by week
  mutate(weekly_avg = mean(sea_water_temperature, na.rm = TRUE))  # computes weekly mean

# calculate loess model
collection_dates <- as.Date(c("2024-07-07"))
loess_fit <- loess(sea_water_temperature ~ as.numeric(date), data = temp)
collections <- data.frame(date = collection_dates,
  loess_fitted = predict(loess_fit, newdata = as.numeric(collection_dates)))

temp %>%
  ggplot(aes(x = as.factor(date), y = sea_water_temperature)) +
  geom_smooth(aes(x = date, y = weekly_avg),method = "loess", color = "salmon4", size = 1)+
  geom_point(aes(x = date, y = sea_water_temperature), color = "salmon4", alpha = 0.1) +
  #geom_point(data = collections, aes(x= date, y = loess_fitted), color = "salmon", size = 4) +  # LOESS y values
  theme_bw()+
  theme(
    strip.background = element_rect(fill = "white"),
    text = element_text(size = 14),
    legend.position = "none") +
    labs(x = expression(Date),
    y = expression(Temperature)
  ) 

```

## quadrat and initial data
```{r}
# mussel size distribution
quadrat %>%
  filter(species == "mussel") %>%
  ggplot(aes(x=shell_length)) + 
  geom_histogram(position="dodge",bins=7,color="white", fill="steelblue4")+
  theme_bw() + theme(axis.text=element_text(size=15),axis.title=element_text(size=18), title = element_text(size=15))+
  labs(x="Shell length (mm)", y="Observations")

summary(mussel_initial) # min and max of collected mussels

# whelk size distribution
quadrat %>%
  filter(species == "whelk") %>%
  ggplot(aes(x=shell_length)) + 
  geom_histogram(position="dodge",bins=7,color="white", fill="lightgoldenrod2")+
  theme_bw() + theme(axis.text=element_text(size=15),axis.title=element_text(size=18), title = element_text(size=15))+
  labs(x="Shell length (mm)", y="Observations")

summary(nucella_initial) # min and max of collected whelks

# whelks in beds
quadrat %>%
  filter(species == "whelk") %>% # keep only whelk data
  distinct(transect, meter, .keep_all = TRUE) %>%  # <- remove duplicates
  ggplot(aes(x = 0, y=density)) + 
    geom_dotplot(binaxis='y', stackdir='center', alpha = 0.1)+
    theme_bw()+
    stat_summary(fun.data=mean_sdl, fun.args = list(mult=1), geom="pointrange", color="black", size = 1)+
    labs(y = "Whelk density in mussel beds")+
    theme(axis.title = element_text(size = 15), axis.text = element_text(size = 15), 
          axis.text.x = element_blank(), axis.title.x = element_blank())

# mussels
quadrat %>%
  filter(species == "mussel") %>% # keep only mussel data
  distinct(transect, meter, .keep_all = TRUE) %>%  # <- remove duplicates
  ggplot(aes(x = 0, y=density)) + 
    geom_dotplot(binaxis='y', stackdir='center', alpha = 0.1)+
    theme_bw()+
    stat_summary(fun.data=mean_sdl, fun.args = list(mult=1), geom="pointrange", color="black", size = 1)+
    labs(y = "Mussel density")+
    theme(axis.title = element_text(size = 15), axis.text = element_text(size = 15), 
          axis.text.x = element_blank(), axis.title.x = element_blank())
```


# Mussels

## Mussel growth - almost an interaction

```{r}
musselrespo <- respo %>%
  filter(Species == "Mussel", !ID == "Shell") # filter just mussel data

musselgrowth <- musselrespo %>%
  mutate(ID = as.numeric(ID)) %>%
  left_join(mussel_initial %>%
            filter(cage == "ctrl"), by = c("ID", "tank")) %>% # bring in mussel initial wet weight with final
  left_join(mussel_final, by = "ID")

musselgrowth <- musselgrowth %>%
  mutate(weight_change = (wet_weight - wet_weight_initial)/wet_weight_initial) # create column for change in weight

musselweight <- lm(weight_change ~ pH * temp_treatment, data=musselgrowth) # model
#plot(musselweight)
anova(musselweight) # nothing sig

# plot
musselweight %>% 
  ggplot(aes(x = pH, y = weight_change, color = as.factor(temp_treatment), fill = as.factor(temp_treatment))) +
  geom_point(alpha = 0.5)+
  geom_smooth(method = "lm", se = TRUE, linetype = "dashed") +
  theme_bw()+
  theme(
    strip.background = element_rect(fill = "white"),
    text = element_text(size = 14)
  ) +
  scale_fill_manual(values = c("salmon", "salmon4")) +
  scale_color_manual(values = c("salmon", "salmon4")) +
    labs(
    x = expression(pH[T]),
    color = "Temperature",
    fill = "Temperature",
    y = expression(ΔWeight(g))
  )

musselgrowth_avg <- musselgrowth %>%
  group_by(pH, temp_treatment) %>%  # group by temp and pH
  summarize(
    avg_weight_change = mean(weight_change, na.rm = TRUE)  # calculate mean growth rate
  )

musselweight_avg <- lm(avg_weight_change ~ pH * temp_treatment, data=musselgrowth_avg) # model
#plot(musselweight)
anova(musselweight) # nothing sig

musselweight_avg %>% 
  ggplot(aes(x = pH, y = avg_weight_change, color = as.factor(temp_treatment), fill = as.factor(temp_treatment))) +
  geom_point(alpha = 0.5)+
  geom_smooth(method = "lm", se = TRUE, linetype = "dashed") +
  theme_bw()+
  theme(
    strip.background = element_rect(fill = "white"),
    text = element_text(size = 14)
  ) +
  scale_fill_manual(values = c("salmon", "salmon4")) +
  scale_color_manual(values = c("salmon", "salmon4")) +
    labs(
    x = expression(pH[T]),
    color = "Temperature",
    fill = "Temperature",
    y = expression(ΔWeight(g))
  )

```

## Mussel shell growth - nothing

```{r}
musselgrowth <- musselgrowth %>%
  mutate(length_change = (shell_length - shell_length_initial)/shell_length_initial) %>%
  mutate(width_change = (shell_width - shell_width_initial)/shell_width_initial) %>%
  mutate(depth_change = (shell_depth - shell_depth_initial)/shell_depth_initial) 

# shell length most often reported

mshellmodelL <- lm(length_change ~ pH * temp_treatment, data = musselgrowth)
#plot(mshellmodelL)
anova(mshellmodelL) # not sig

mshellmodelL %>% 
  ggplot(aes(x = pH, y = length_change, color = as.factor(temp_treatment), fill = as.factor(temp_treatment))) +
  geom_point(alpha = 0.5)+
  geom_smooth(method = "lm", se = TRUE, linetype = "dashed") +
  theme_bw()+
  theme(
    strip.background = element_rect(fill = "white"),
    text = element_text(size = 14)
  ) +
  scale_fill_manual(values = c("salmon", "salmon4")) +
  scale_color_manual(values = c("salmon", "salmon4")) +
    labs(
    x = expression(pH[T]),
    color = "Temperature",
    fill = "Temperature",
    y = expression(ΔShell~length(mm))
  )

# shell width

mshellmodelW <- lm(width_change ~ pH * temp_treatment, data = musselgrowth)
#plot(mshellmodelW)
anova(mshellmodelW) # not sig

mshellmodelW %>% 
  ggplot(aes(x = pH, y = width_change, color = as.factor(temp_treatment), fill = as.factor(temp_treatment))) +
  geom_point(alpha = 0.5)+
  geom_smooth(method = "lm", se = TRUE, linetype = "dashed") +
  theme_bw()+
  theme(
    strip.background = element_rect(fill = "white"),
    text = element_text(size = 14)
  ) +
  scale_fill_manual(values = c("salmon", "salmon4")) +
  scale_color_manual(values = c("salmon", "salmon4")) +
    labs(
    x = expression(pH[T]),
    color = "Temperature",
    fill = "Temperature",
    y = expression(ΔShell~width(mm))
  )

# shell depth 
mshellmodelD <- lm(depth_change ~ pH * temp_treatment, data = musselgrowth)
#plot(mshellmodelD)
anova(mshellmodelD) # not sig

mshellmodelD %>% 
  ggplot(aes(x = pH, y = depth_change, color = as.factor(temp_treatment), fill = as.factor(temp_treatment))) +
  geom_point(alpha = 0.5)+
  geom_smooth(method = "lm", se = TRUE, linetype = "dashed") +
  theme_bw()+
  theme(
    strip.background = element_rect(fill = "white"),
    text = element_text(size = 14)
  ) +
  scale_fill_manual(values = c("salmon", "salmon4")) +
  scale_color_manual(values = c("salmon", "salmon4")) +
    labs(
    x = expression(pH[T]),
    color = "Temperature",
    fill = "Temperature",
    y = expression(ΔShell~depth(mm))
  )
```

## Mussel Condition Index - nothing

```{r}
musselgrowth$CI <- musselgrowth$AFDW/musselgrowth$dry_shell*100
mCImodel <- lm(CI ~ pH * temp_treatment, data = musselgrowth)
#plot(mCImodel)
anova(mCImodel)

mCImodel %>% 
  ggplot(aes(x = pH, y = CI, color = as.factor(temp_treatment), fill = as.factor(temp_treatment))) +
  geom_point(alpha = 0.5)+
  geom_smooth(method = "lm", se = TRUE, linetype = "dashed") +
  theme_bw()+
  theme(
    strip.background = element_rect(fill = "white"),
    text = element_text(size = 14)
  ) +
  scale_fill_manual(values = c("salmon", "salmon4")) +
  scale_color_manual(values = c("salmon", "salmon4")) +
    labs(
    x = expression(pH[T]),
    color = "Temperature",
    fill = "Temperature",
    y = expression(Condition~Index)
  )

# averages
musselgrowth <- musselgrowth %>%
  group_by(pH, temp_treatment) %>%  # group by temp and pH
  summarize(
    avg_CI = mean(CI, na.rm = TRUE)  # calculate mean growth rate
  )

mCImodel_avg <- lm(avg_CI ~ pH * temp_treatment, data=musselgrowth) # model
#plot(musselweight)
anova(mCImodel_avg) # nothing sig

mCImodel_avg %>% 
  ggplot(aes(x = pH, y = avg_CI, color = as.factor(temp_treatment), fill = as.factor(temp_treatment))) +
  geom_point(alpha = 0.5)+
  geom_smooth(method = "lm", se = TRUE, linetype = "dashed") +
  theme_bw()+
  theme(
    strip.background = element_rect(fill = "white"),
    text = element_text(size = 14)
  ) +
  scale_fill_manual(values = c("salmon", "salmon4")) +
  scale_color_manual(values = c("salmon", "salmon4")) +
    labs(
    x = expression(pH[T]),
    color = "Temperature",
    fill = "Temperature",
    y = expression(Condition~Index)
  )
```

## Mussel calcification - pH significant at low temperature (but likely driven by those low points)
```{r}
mussel_calc <- calc %>%
  filter(Species == "Mussel") %>%
  mutate(ID = as.factor(ID)) %>%
  left_join(musselrespo %>%
              select(tank, pH) %>%
              distinct(),
              by = "tank") %>%
  mutate(temp_treatment = as.factor(temp_treatment))

Mcalc_lm <- lm(umol.cm2.hr ~ wet_weight, data=calc)
summary(Mcalc_lm) # wet weight does not predict calc

# model calc 
Mcalcmodel <- lm(umol.cm2.hr ~ pH * temp_treatment, data = mussel_calc)
#plot(Mcalcmodel)
anova(Mcalcmodel) # pH sig

# normal plot
Mcalcmodel %>%
  ggplot(aes(x=pH, y=umol.cm2.hr, color = as.factor(temp_treatment),fill=as.factor(temp_treatment)))+
  geom_point(alpha = 0.5)+
  theme_bw() +
  theme(strip.background = element_rect(fill = "white"),
        text = element_text(size = 14)) +
  scale_fill_manual(values = c("salmon", "salmon4")) +
  scale_color_manual(values = c("salmon", "salmon4")) +
  labs(x = expression(pH[T]),
       color = "Temperature",
       fill = "Temperature",
       y = expression(Calcification~rate~(CaCO[3]~g^-1~hr^-1)))

# average
mussel_calc_avg <- mussel_calc %>%
  group_by(pH, temp_treatment) %>%  # group by temp and pH
  summarize(
    avg_calc = mean(umol.cm2.hr , na.rm = TRUE)  # calculate mean calc rate
  )

mCalcmodel_avg <- lm(avg_calc ~ pH * temp_treatment, data=mussel_calc_avg) # model
#plot(musselweight)
anova(mCalcmodel_avg) # nothing sig

# average plot
Mcalcplot <-
mussel_calc_avg %>%
  ggplot(aes(x=pH, y=avg_calc, color = temp_treatment, fill= temp_treatment))+
  geom_point(alpha = 0.5, aes(shape = temp_treatment))+
  geom_hline(yintercept = 0, linetype = "dashed") +
  theme_bw() +
  theme(strip.background = element_rect(fill = "white"),
        text = element_text(size = 14)) +
  scale_fill_manual(values = c("#0072B2", "#D55E00")) +
  scale_color_manual(values = c("#0072B2", "#D55E00")) +
  labs(x = expression(pH[T]),
       color = expression(paste("Temperature ",degree,"C")),
       fill = expression(paste("Temperature ",degree,"C")),
       shape = expression(paste("Temperature ",degree,"C")),
       y = expression(Calcification~rate~(mu*mol~CaCO[3]~g^-1~hr^-1)))

```

## Mussel wet to dry - bad

```{r}
musselreg <- lm(AFDW ~ wet_weight, data=musselrespo) # how well does wet weight predict afdw?

summary(musselreg) # r^2 = 0.5

musselreg %>% 
  ggplot(aes(x = wet_weight, y = AFDW)) +
  geom_point(alpha = 0.5)+
  geom_smooth(method = "lm", se = TRUE) +
  theme_bw()+
  theme(
    strip.background = element_rect(fill = "white"),
    text = element_text(size = 14)
  ) +
    labs(
    x = expression(wet~weight),
    y = "AFDW")
```

## Mussel respo - nothing
```{r}
# check if weight is driving respo
musrespoweight <- lm(Respiration ~ AFDW, data=musselrespo) # does AFDW predict respiration rate?
#plot(musrespoweight)
musselrespo <- musselrespo %>%
  mutate(model = predict(musrespoweight))
anova(musrespoweight) # weight significant

musselrespo %>%
  ggplot(aes(x=AFDW, y=Respiration))+
  stat_summary(aes(color = as.factor(temp_treatment)), 
               fun.data = mean_se, fun.args = list(mult = 1), size = 0.5) +
  geom_line(aes(y = model)) +
  theme_bw() +
  theme(strip.background = element_rect(fill = "white"),
        text = element_text(size = 14)) +
  scale_fill_manual(values = c("salmon", "salmon4")) +
  scale_color_manual(values = c("salmon", "salmon4"))+ 
  labs(x = expression(Dry~Weight~(g)),
      color = "Temperature",
      fill = "Temperature",
      y = expression(Respiration~rate~(mu*mol~O[2]~g^-1~hr^-1)))

# add size as a covariate
musselresmodel <- lm(Respiration ~ pH * temp_treatment + AFDW, data = musselrespo)
#plot(musselresmodel)
anova(musselresmodel)

musselresmodel %>%
  ggplot(aes(x=pH, y=Respiration, color = as.factor(temp_treatment),fill=as.factor(temp_treatment)))+
  geom_point(alpha = 0.5)+
  geom_smooth(method = "lm", se = TRUE, linetype = "dashed") +
  theme_bw() +
  theme(strip.background = element_rect(fill = "white"),
        text = element_text(size = 14)) +
  scale_fill_manual(values = c("salmon", "salmon4")) +
  scale_color_manual(values = c("salmon", "salmon4")) +
  labs(x = expression(pH[T]),
       color = "Temperature",
       fill = "Temperature",
       y = expression(Respiration~rate~(mu*mol~O[2]~g^-1~hr^-1)))

# averages
musselrespo_average <- musselrespo %>%
  group_by(pH, temp_treatment) %>%  # group by temp and pH
  summarize(
    avg_respo = mean(Respiration , na.rm = TRUE)  # calculate mean respo rate
  )

mresmodel_avg <- lm(avg_respo ~ pH * temp_treatment, data=musselrespo_average) # model
#plot(musselweight)
anova(mresmodel_avg) # nothing sig

# average plot
Mrespoplot <-
mresmodel_avg %>%
  ggplot(aes(x=pH, y=avg_respo, color = temp_treatment, fill = temp_treatment))+
  geom_point(alpha = 0.5, aes(shape = temp_treatment))+
  theme_bw() +
  theme(strip.background = element_rect(fill = "white"),
        text = element_text(size = 14)) +
  scale_fill_manual(values = c("#0072B2", "#D55E00")) +
  scale_color_manual(values = c("#0072B2", "#D55E00")) +
  labs(x = expression(pH[T]),
       color = expression(paste("Temperature ",degree,"C")),
       fill = expression(paste("Temperature ",degree,"C")),
       shape = expression(paste("Temperature ",degree,"C")),
       y = expression(Respiration~rate~(mu*mol~O[2]~g^-1~hr^-1)))
```

### Respo trim test

```{r}
musselrespo_trimmed <- musselrespo_trimmed %>%
  filter(Species == "Mussel") %>%
  mutate(temp_treatment = as.factor(temp_treatment))

musselrespotrimtest <- bind_rows(list(a = musselrespo, b = musselrespo_trimmed), .id = "id")

t.test(Respiration ~ id, data = musselrespotrimtest)
```

## C:R

```{r}
mussel_avg <- mussel_calc_avg %>%
  left_join(musselrespo_average)

mussel_avg %>%
  ggplot(aes(x = avg_calc, y = avg_respo, color = as.factor(temp_treatment), fill = as.factor(temp_treatment))) +
  geom_point(alpha = 0.5)+
  geom_smooth(method = "lm", se = TRUE) +
  theme_bw()+
  theme(
    strip.background = element_rect(fill = "white"),
    text = element_text(size = 14)
  ) +
  scale_fill_manual(values = c("#0072B2", "#D55E00")) +
  scale_color_manual(values = c("#0072B2", "#D55E00")) +
    labs(
    x = expression(Calcification~rate~(mu*mol~CaCO[3]~g^-1~hr^-1)),
    color = "Temperature",
    fill = "Temperature",
    y = expression(Respiration~rate~(mu*mol~O[2]~g^-1~hr^-1)))
```

# Nucella

## Nucella growth - almost temp

```{r}
nucellarespo <- respo %>%
  filter(Species == "Nucella", !ID == "Shell") # filter just nucella data

nucellagrowth <- nucellarespo %>%
  mutate(ID = as.numeric(ID)) %>%
  left_join(nucella_initial %>%
              dplyr::select(c("ID", "wet_weight_initial", "shell_length_initial", "shell_width_initial")), by = c("ID")) %>% # bring in nucella initial wet weight and shell measurements
  left_join(nucella_final %>%
              dplyr::select(c("ID", "dry_weight", "shell_length", "shell_width", "shell_growth", "dry_shell")), by = "ID") # bring in dry weight and final shell measurements

nucellagrowth <- nucellagrowth %>%
  mutate(weight_change = (wet_weight - wet_weight_initial)/wet_weight_initial) # create column for change in wet weight

nucellaweight <- lm(weight_change ~ pH * temp_treatment, data=nucellagrowth) # model
#plot(nucellaweight)
anova(nucellaweight) # almost temp effect

# plot
nucellaweight %>% 
  ggplot(aes(x = pH, y = weight_change, color = as.factor(temp_treatment), fill = as.factor(temp_treatment))) +
  geom_point(alpha = 0.5)+
  geom_smooth(method = "lm", se = TRUE) +
  theme_bw()+
  theme(
    strip.background = element_rect(fill = "white"),
    text = element_text(size = 14)
  ) +
  scale_fill_manual(values = c("salmon", "salmon4")) +
  scale_color_manual(values = c("salmon", "salmon4")) +
    labs(
    x = expression(pH[T]),
    color = "Temperature",
    fill = "Temperature",
    y = expression(ΔWeight(g))
  )

# average
nucellagrowth_avg <- nucellagrowth %>%
  group_by(pH, temp_treatment) %>%  # group by temp and pH
  summarize(
    avg_growth = mean(weight_change , na.rm = TRUE)  # calculate mean growth rate
  )

ngrowth_avg <- lm(avg_growth ~ pH * temp_treatment, data=nucellagrowth_avg) # model
#plot(musselweight)
anova(ngrowth_avg) # nothing sig

# average plot
ngrowth_avg %>%
  ggplot(aes(x=pH, y=avg_growth, color = as.factor(temp_treatment),fill=as.factor(temp_treatment)))+
  geom_point(alpha = 0.5)+
  geom_smooth(method = "lm", se = TRUE, linetype = "dashed") +
  theme_bw() +
  theme(strip.background = element_rect(fill = "white"),
        text = element_text(size = 14)) +
  scale_fill_manual(values = c("salmon", "salmon4")) +
  scale_color_manual(values = c("salmon", "salmon4")) +
  labs(x = expression(pH[T]),
       color = "Temperature",
       fill = "Temperature",
       y = expression(ΔWeight(g)))
```

## Nucella shell growth - temp effect!

```{r}
nucellagrowth <- nucellagrowth %>%
  mutate(length_change = (shell_length - shell_length_initial)/shell_length_initial) %>%
  mutate(width_change = (shell_width - shell_width_initial)/shell_width_initial)

# shell length 

nshellmodelL <- lm(length_change ~ pH * temp_treatment, data = nucellagrowth)
#plot(nshellmodelL)
anova(nshellmodelL) # temp sig

nshellmodelL %>% 
  ggplot(aes(x = pH, y = length_change, color = as.factor(temp_treatment), fill = as.factor(temp_treatment))) +
  geom_point(alpha = 0.5)+
  geom_smooth(method = "lm", se = TRUE) +
  theme_bw()+
  theme(
    strip.background = element_rect(fill = "white"),
    text = element_text(size = 14)
  ) +
  scale_fill_manual(values = c("salmon", "salmon4")) +
  scale_color_manual(values = c("salmon", "salmon4")) +
    labs(
    x = expression(pH[T]),
    color = "Temperature",
    fill = "Temperature",
    y = expression(ΔShell~length~(mm))
  )

# average
nucellagrowth_avg <- nucellagrowth %>%
  group_by(pH, temp_treatment) %>%  # group by temp and pH
  summarize(
    avg_shellL = mean(length_change , na.rm = TRUE)  # calculate mean growth rate
  )

nshellL_avg <- lm(avg_shellL ~ pH * temp_treatment, data=nucellagrowth_avg) # model
#plot(musselweight)
anova(nshellL_avg) # nothing sig

# average plot
nshellL_avg %>%
  ggplot(aes(x=pH, y=avg_shellL, color = as.factor(temp_treatment),fill=as.factor(temp_treatment)))+
  geom_point(alpha = 0.5)+
  geom_smooth(method = "lm", se = TRUE, linetype = "dashed") +
  theme_bw() +
  theme(strip.background = element_rect(fill = "white"),
        text = element_text(size = 14)) +
  scale_fill_manual(values = c("salmon", "salmon4")) +
  scale_color_manual(values = c("salmon", "salmon4")) +
  labs(x = expression(pH[T]),
       color = "Temperature",
       fill = "Temperature",
       y =  expression(ΔShell~length~(mm)))

# shell width

nshellmodelW <- lm(width_change ~ pH * temp_treatment, data = nucellagrowth)
#plot(nshellmodelW)
anova(nshellmodelW) # temp sig

nshellmodelW %>% 
  ggplot(aes(x = pH, y = width_change, color = as.factor(temp_treatment), fill = as.factor(temp_treatment))) +
  geom_point(alpha = 0.5)+
  geom_smooth(method = "lm", se = TRUE) +
  theme_bw()+
  theme(
    strip.background = element_rect(fill = "white"),
    text = element_text(size = 14)
  ) +
  scale_fill_manual(values = c("salmon", "salmon4")) +
  scale_color_manual(values = c("salmon", "salmon4")) +
    labs(
    x = expression(pH[T]),
    color = "Temperature",
    fill = "Temperature",
    y = expression(ΔShell~width~(mm))
  )

# average
nucellagrowth_avg <- nucellagrowth %>%
  group_by(pH, temp_treatment) %>%  # group by temp and pH
  summarize(
    avg_shellW = mean(width_change , na.rm = TRUE)  # calculate mean growth rate
  )

nshellW_avg <- lm(avg_shellW ~ pH * temp_treatment, data=nucellagrowth_avg) # model
#plot(musselweight)
anova(nshellW_avg) # temp significant

# average plot
nshellW_avg %>%
  ggplot(aes(x=pH, y=avg_shellW, color = as.factor(temp_treatment),fill=as.factor(temp_treatment)))+
  geom_point(alpha = 0.5)+
  geom_smooth(method = "lm", se = TRUE) +
  theme_bw() +
  theme(strip.background = element_rect(fill = "white"),
        text = element_text(size = 14)) +
  scale_fill_manual(values = c("salmon", "salmon4")) +
  scale_color_manual(values = c("salmon", "salmon4")) +
  labs(x = expression(pH[T]),
       color = "Temperature",
       fill = "Temperature",
       y =  expression(ΔShell~width~(mm)))
       
# shell growth estimated using nail polish

nshellmodelNP <- lm(shell_growth ~ pH * temp_treatment, data = nucellagrowth)
#plot(nshellmodelNP)
anova(nshellmodelNP) # temp treatment

nshellmodelNP %>% 
  ggplot(aes(x = pH, y = shell_growth, color = as.factor(temp_treatment), fill = as.factor(temp_treatment))) +
  geom_point(alpha = 0.5)+
  geom_smooth(method = "lm", se = TRUE) +
  theme_bw()+
  theme(
    strip.background = element_rect(fill = "white"),
    text = element_text(size = 14)
  ) +
  scale_fill_manual(values = c("salmon", "salmon4")) +
  scale_color_manual(values = c("salmon", "salmon4")) +
    labs(
    x = expression(pH[T]),
    color = "Temperature",
    fill = "Temperature",
    y = expression(ΔShell~growth~(mm)))

nucellagrowth_avg <- nucellagrowth %>%
  group_by(pH, temp_treatment) %>%  # group by temp and pH
  summarize(
    avg_shellG = mean(shell_growth , na.rm = TRUE)  # calculate mean growth rate
  )

nshellG_avg <- lm(avg_shellG ~ pH * temp_treatment, data=nucellagrowth_avg) # model
#plot(nShellG_avgna)
anova(nshellG_avg) # temp significant

# average plot
nshellG_avg %>%
  ggplot(aes(x=pH, y=avg_shellG, color = as.factor(temp_treatment),fill=as.factor(temp_treatment)))+
  geom_point(alpha = 0.5)+
  geom_smooth(method = "lm", se = TRUE) +
  theme_bw() +
  theme(strip.background = element_rect(fill = "white"),
        text = element_text(size = 14)) +
  scale_fill_manual(values = c("salmon", "salmon4")) +
  scale_color_manual(values = c("salmon", "salmon4")) +
  labs(x = expression(pH[T]),
       color = "Temperature",
       fill = "Temperature",
       y =  expression(ΔShell~growth~(mm)))

# without pH
shellgrowthplot <-
nshellG_avg %>% 
  ggplot(aes(x =temp_treatment , y = avg_shellG)) +
  geom_boxplot(alpha=0.5, outlier.alpha=0) + 
  geom_jitter(aes(fill = as.numeric(pH)),width=0.25, pch=21, size=2) +
  scale_fill_gradient(low = "palegreen2", high = "#0072B2")+
  theme_bw()+
  theme(
    strip.background = element_rect(fill = "white"),
    text = element_text(size = 14)
  ) +
    labs(
    x = expression(paste("Temperature ",degree,"C")),
    fill = "pH",
    y =  expression(ΔShell~growth~(mm))) 

# diff in temp treatments
nucellagrowth %>%
  group_by(temp_treatment) %>%
  summarise(mean_value = mean(shell_growth, na.rm = TRUE))
```

## Nucella Condition Index - not sig

```{r}
nucellagrowth$CI <- nucellagrowth$AFDW/nucellagrowth$dry_shell*100
nCImodel <- lm(CI ~ pH * temp_treatment, data = nucellagrowth)
#plot(mCImodel)
anova(mCImodel)

nCImodel %>% 
  ggplot(aes(x = pH, y = CI, color = as.factor(temp_treatment), fill = as.factor(temp_treatment))) +
  geom_point(alpha = 0.5)+
  geom_smooth(method = "lm", se = TRUE, linetype = "dashed") +
  theme_bw()+
  theme(
    strip.background = element_rect(fill = "white"),
    text = element_text(size = 14)
  ) +
  scale_fill_manual(values = c("salmon", "salmon4")) +
  scale_color_manual(values = c("salmon", "salmon4")) +
    labs(
    x = expression(pH[T]),
    color = "Temperature",
    fill = "Temperature",
    y = expression(Condition~Index)
  )

# averages
nucellagrowth_avg <- nucellagrowth %>%
  group_by(pH, temp_treatment) %>%  # group by temp and pH
  summarize(
    avg_CI = mean(CI, na.rm = TRUE)  # calculate mean growth rate
  )

nCImodel_avg <- lm(avg_CI ~ pH * temp_treatment, data=nucellagrowth_avg) # model
#plot(musselweight)
anova(nCImodel_avg) # nothing sig

nCImodel_avg %>% 
  ggplot(aes(x = pH, y = avg_CI, color = as.factor(temp_treatment), fill = as.factor(temp_treatment))) +
  geom_point(alpha = 0.5)+
  geom_smooth(method = "lm", se = TRUE, linetype = "dashed") +
  theme_bw()+
  theme(
    strip.background = element_rect(fill = "white"),
    text = element_text(size = 14)
  ) +
  scale_fill_manual(values = c("salmon", "salmon4")) +
  scale_color_manual(values = c("salmon", "salmon4")) +
    labs(
    x = expression(pH[T]),
    color = "Temperature",
    fill = "Temperature",
    y = expression(Condition~Index)
  )
```

## Nucella calcification - temp effect! 
```{r}
nucella_calc <- calc %>%
  filter(Species == "Nucella") %>%
  mutate(ID = as.factor(ID)) %>%
  left_join(nucellarespo %>% 
              select(ID,pH)) %>%
  mutate(temp_treatment = as.factor(temp_treatment))

Ncalc_lm <- lm(umol.cm2.hr ~ wet_weight, data=calc)
summary(Ncalc_lm) # wet weight does not predict calc

# model calc with all interaction terms
Ncalcmodel <- lm(umol.cm2.hr ~ pH * temp_treatment, data = nucella_calc)
#plot(Ncalcmodel)
anova(Ncalcmodel) # temp sig

# normal plot
Ncalcmodel %>%
  ggplot(aes(x=pH, y=umol.cm2.hr, color = as.factor(temp_treatment),fill=as.factor(temp_treatment)))+
  geom_point(alpha = 0.5)+
  geom_smooth(method = "lm", se = TRUE) +
  theme_bw() +
  theme(strip.background = element_rect(fill = "white"),
        text = element_text(size = 14)) +
  scale_fill_manual(values = c("salmon", "salmon4")) +
  scale_color_manual(values = c("salmon", "salmon4")) +
  labs(x = expression(pH[T]),
       color = "Temperature",
       fill = "Temperature",
       y = expression(Calcification~rate~(CaCO[3]~g^-1~hr^-1)))

# averages
nucellacalc_avg <- nucella_calc %>%
  group_by(pH, temp_treatment) %>%  # group by temp and pH
  summarize(
    avg_calc = mean(umol.cm2.hr, na.rm = TRUE)  # calculate mean growth rate
  )

ncalcmodel_avg <- lm(avg_calc ~ pH * temp_treatment, data=nucellacalc_avg) # model
#plot(musselweight)
anova(ncalcmodel_avg) # temperature 

ncalcmodel_avg %>% 
  ggplot(aes(x = pH, y = avg_calc, color = as.factor(temp_treatment), fill = as.factor(temp_treatment))) +
  geom_point(alpha = 0.5)+
  geom_smooth(method = "lm", se = TRUE) +
  theme_bw()+
  theme(
    strip.background = element_rect(fill = "white"),
    text = element_text(size = 14)
  ) +
  scale_fill_manual(values = c("salmon", "salmon4")) +
  scale_color_manual(values = c("salmon", "salmon4")) +
    labs(
    x = expression(pH[T]),
    color = "Temperature",
    fill = "Temperature",
    y = expression(Calcification~rate~(mu*mol~CaCO[3]~g^-1~hr^-1)))

# without pH
Ncalcplot <-
ncalcmodel_avg %>% 
  ggplot(aes(x = temp_treatment, y = avg_calc)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_boxplot(alpha=0.5, outlier.alpha=0) + 
  geom_jitter(aes(fill = as.numeric(pH)),width=0.25, pch=21, size=2) +
  scale_fill_gradient(low = "palegreen2", high = "#0072B2")+
  theme_bw()+
  theme(
    strip.background = element_rect(fill = "white"),
    text = element_text(size = 14)
  ) +
    labs(
    x = expression(paste("Temperature ",degree,"C")),
    fill = "pH",
     y = expression(Calcification~rate~(mu*mol~CaCO[3]~g^-1~hr^-1)))

# diff between temp treatments
nucella_calc %>%
  group_by(temp_treatment) %>%
  summarise(mean_value = mean(umol.cm2.hr, na.rm = TRUE))
```

## Nucella respo - temperature significant again but opposite of what i expected

```{r}
# does weight matter? no
nucrespoweight <- lm(Respiration ~ AFDW, data = nucellarespo) # does AFDW predict respiration rate?
#plot(nucrespoweight)
anova(nucrespoweight) # weight not significant

nucellarespo %>%
  ggplot(aes(x=AFDW, y=Respiration))+
  stat_summary(aes(color = as.factor(temp_treatment)), fun.args = list(mult = 1), size = 0.5) +
  theme_bw() +
  theme(strip.background = element_rect(fill = "white"),
        text = element_text(size = 14)) +
  scale_fill_manual(values = c("salmon", "salmon4")) +
  scale_color_manual(values = c("salmon", "salmon4"))+ 
  labs(x = expression(Dry~Weight~(g)),
      color = "Temperature",
      fill = "Temperature",
      y = expression(Respiration~rate~(mu*mol~O[2]~g^-1~hr^-1)))

# can use raw data
nucrespomodel <- lm(Respiration ~ pH * temp_treatment, data = nucellarespo)
#plot(nucrespomodel)
anova(nucrespomodel) # temp sig

nucrespomodel %>% 
  ggplot(aes(x = pH, y = Respiration, color = as.factor(temp_treatment), fill = as.factor(temp_treatment))) +
  geom_point(alpha = 0.5)+
  geom_smooth(method = "lm", se = TRUE) +
  theme_bw()+
  theme(
    strip.background = element_rect(fill = "white"),
    text = element_text(size = 14)
  ) +
  scale_fill_manual(values = c("salmon", "salmon4")) +
  scale_color_manual(values = c("salmon", "salmon4")) +
    labs(
    x = expression(pH[T]),
    color = "Temperature",
    fill = "Temperature",
    y = expression(Respiration~rate~(mu*mol~O[2]~g^-1~hr^-1))
  )

# averages
nucellarespo_avg <- nucellarespo %>%
  group_by(pH, temp_treatment) %>%  # group by temp and pH
  summarize(
    avg_respo = mean(Respiration, na.rm = TRUE)  # calculate mean growth rate
  )

nucrespoavg <- lm(avg_respo ~ pH * temp_treatment, data=nucellarespo_avg) # model
#plot(musselweight)
anova(nucrespoavg) # temperature 
summary(nucrespoavg)

nucrespoavg %>% 
  ggplot(aes(x = pH, y = avg_respo, color = as.factor(temp_treatment), fill = as.factor(temp_treatment))) +
  geom_point(alpha = 0.5)+
  geom_smooth(method = "lm", se = TRUE) +
  theme_bw()+
  theme(
    strip.background = element_rect(fill = "white"),
    text = element_text(size = 14)
  ) +
  scale_fill_manual(values = c("salmon", "salmon4")) +
  scale_color_manual(values = c("salmon", "salmon4")) +
    labs(
    x = expression(pH[T]),
    color = "Temperature",
    fill = "Temperature",
    y = expression(Respiration~rate~(mu*mol~O[2]~g^-1~hr^-1)))

# without pH
Nrespoplot <-
nucrespoavg %>% 
  ggplot(aes(x = temp_treatment, y = avg_respo)) +
  geom_boxplot(alpha=0.5, outlier.alpha=0) + 
  geom_jitter(aes(fill = as.numeric(pH)),width=0.25, pch=21, size=2) +
  scale_fill_gradient(low = "palegreen2", high = "#0072B2")+
  theme_bw()+
  theme(
    strip.background = element_rect(fill = "white"),
    text = element_text(size = 14)
  ) +
    labs(
    x = expression(paste("Temperature ",degree,"C")),
    fill = "pH",
    y = expression(Respiration~rate~(mu*mol~O[2]~g^-1~hr^-1)))

# diff between temps
nucellarespo %>%
  group_by(temp_treatment) %>%
  summarise(mean_value = mean(Respiration, na.rm = TRUE))
```

## C:R

```{r}
nucella_avg <- nucellacalc_avg %>%
  left_join(nucellarespo_avg)

nucella_avg %>%
  ggplot(aes(x = avg_respo, y = avg_calc, color = as.factor(temp_treatment), fill = as.factor(temp_treatment))) +
  geom_point(alpha = 0.5)+
  geom_smooth(method = "lm", se = TRUE) +
  theme_bw()+
  theme(
    strip.background = element_rect(fill = "white"),
    text = element_text(size = 14)
  ) +
  scale_fill_manual(values = c("#0072B2", "#D55E00")) +
  scale_color_manual(values = c("#0072B2", "#D55E00")) +
    labs(
    y = expression(Calcification~rate~(mu*mol~CaCO[3]~g^-1~hr^-1)),
    color = "Temperature",
    fill = "Temperature",
    x = expression(Respiration~rate~(mu*mol~O[2]~g^-1~hr^-1)))
```

# Nucella mortality

```{r}
nucellaMortality <- nucellarespo %>%
  group_by(tank) %>%
  summarise(mortalities = 5-n())
```

# Predation

## number eaten - potential increase with pH, but driven very strongly by 8.0/22
```{r}
predation <- mortality %>%
  filter(eaten == "Y") %>%
  group_by(tank) %>%
  summarise(mortalities = n()) %>%
  left_join(musselrespo %>%
            group_by(tank) %>%
            summarise(pH = mean(pH, na.rm = TRUE),
                      temp_treatment = first(temp_treatment)))  # add treatment data

predationmodel <- lm(mortalities ~ pH * temp_treatment, data = predation)
#plot(predationmodel)
anova(predationmodel) # effect of pH?

predation %>%
  ggplot(aes(x = pH, y = mortalities, color = as.factor(temp_treatment), fill = as.factor(temp_treatment))) +
  geom_point(alpha = 0.5)+
  geom_smooth(method = "lm", se = TRUE) +
  theme_bw()+
  theme(
    strip.background = element_rect(fill = "white"),
    text = element_text(size = 14)
  ) +
  scale_fill_manual(values = c("salmon", "salmon4")) +
  scale_color_manual(values = c("salmon", "salmon4")) +
    labs(
    x = expression(pH[T]),
    color = "Temperature",
    fill = "Temperature",
    y = "Mussels eaten")

```

## Biomass eaten
```{r}
predation <- mortality %>%
  filter(eaten == "Y") %>% # filter out eaten mussels
  group_by(tank) %>%
  summarise(biomass_eaten = sum(wet_weight, na.rm = TRUE)) %>% # biomass eaten per tank
  left_join(musselrespo %>%
            group_by(tank) %>%
            summarise(pH = mean(pH, na.rm = TRUE),
                      temp_treatment = first(temp_treatment)))  # add treatment data

predation_bmodel <- lm(biomass_eaten ~ pH * temp_treatment, data = predation)
plot(predation_bmodel)
anova(predation_bmodel) # nothing

eatenplot <- 
predation %>%
  ggplot(aes(x = pH, y = biomass_eaten)) +
  geom_point(alpha = 0.5, aes(color = as.factor(temp_treatment), fill = as.factor(temp_treatment)))+
  #geom_smooth(method = "lm", se = TRUE, color = "black", fill = "gray70") +
  theme_bw()+
  theme(
    strip.background = element_rect(fill = "white"),
    text = element_text(size = 14)
  ) +
  scale_fill_manual(values = c("#0072B2", "#D55E00")) +
  scale_color_manual(values = c("#0072B2", "#D55E00")) +
    labs(
    x = expression(pH[T]),
    color = expression(paste("Temperature ",degree,"C")),
    fill = expression(paste("Temperature ",degree,"C")),
    y = "Biomass of mussels eaten (g)")
```

## Predation - biomass eaten standardized to control
```{r}
mortality_ctrl <- mortality %>%
  filter(cage == "ctrl") %>%
  group_by(tank) %>%
  summarise(biomass_lost = sum(wet_weight, na.rm = TRUE)) # get all the control mortality biomass per tank

predation <- mortality %>%
  filter(eaten == "Y") %>%
  group_by(tank) %>%
  summarise(biomass_eaten = sum(wet_weight, na.rm = TRUE)) %>% # biomass eaten per tank
  left_join(mortality_ctrl, by = "tank") %>%
  left_join(musselrespo %>%
              group_by(tank) %>%
              summarise(pH = mean(pH, na.rm = TRUE), # add real treatment values
temp_treatment = first(temp_treatment)),by = "tank") %>%
  replace_na(list(biomass_lost = 0)) %>%  # replace NA with 0
  mutate(eaten_lost = (biomass_eaten+1)/(biomass_lost+1)) # add 1 to get rid of 0 values

predation_b_n_model <- lm(eaten_lost ~ pH * temp_treatment, data = predation)
plot(predation_b_n_model)
anova(predation_b_n_model) # nothing

predation %>%
  ggplot(aes(x = pH, y = eaten_lost)) +
  geom_point(alpha = 0.5, aes(color = as.factor(temp_treatment), fill = as.factor(temp_treatment)))+
  geom_smooth(method = "lm", se = TRUE, color = "black", fill = "gray70") +
  theme_bw()+
  theme(
    strip.background = element_rect(fill = "white"),
    text = element_text(size = 14)
  ) +
  scale_fill_manual(values = c("#0072B2", "#D55E00")) +
  scale_color_manual(values = c("#0072B2", "#D55E00")) +
    labs(x = expression(pH[T]),
    color = expression(paste("Temperature ",degree,"C")),
    fill = expression(paste("Temperature ",degree,"C")),
    y = "Biomass of mussels eaten (g)")
```


## Mortality
```{r}
# using count
mortality_c <- mortality %>%
  filter(cage == "ctrl") %>%
  group_by(tank) %>%
  summarise(ctrlmortality = n(), .groups = "drop") %>% # count number of mortalities per tank
  replace_na(list(ctrlmortality = 0))  # replace NA with 0

predation <- predation %>% 
  left_join(mortality_c, by = "tank") %>%
  replace_na(list(ctrlmortality = 0))  # replace NA with 0

ctrlMtest <- lm(ctrlmortality ~ pH * temp_treatment, data = predation)
#plot(predationmodel)
anova(ctrlMtest)

predation %>%
  ggplot(aes(x = pH, y = ctrlmortality, color = as.factor(temp_treatment), fill = as.factor(temp_treatment))) +
  geom_point(alpha = 0.5)+
  geom_smooth(method = "lm", se = TRUE) +
  theme_bw()+
  theme(
    strip.background = element_rect(fill = "white"),
    text = element_text(size = 14)
  ) +
  scale_fill_manual(values = c("salmon", "salmon4")) +
  scale_color_manual(values = c("salmon", "salmon4")) +
    labs(
    x = expression(pH[T]),
    color = "Temperature",
    fill = "Temperature",
    y = "Control mussels dead")

# what if we did biomass rather than count

mortalitytest <- lm(biomass_lost ~ pH * temp_treatment, data = predation)
#plot(predationmodel)
anova(mortalitytest)

predation %>%
  ggplot(aes(x = pH, y = biomass_lost, color = as.factor(temp_treatment), fill = as.factor(temp_treatment))) +
  geom_point(alpha = 0.5)+
  geom_smooth(method = "lm", se = TRUE) +
  theme_bw()+
  theme(
    strip.background = element_rect(fill = "white"),
    text = element_text(size = 14)
  ) +
  scale_fill_manual(values = c("salmon", "salmon4")) +
  scale_color_manual(values = c("salmon", "salmon4")) +
    labs(
    x = expression(pH[T]),
    color = "Temperature",
    fill = "Temperature",
    y = "Control mussels dead")
```

## Drilled mussels
```{r}
predation_d <- mortality %>%
  filter(eaten == "Y") %>%
  mutate(drilled = as.factor(drilled)) %>%
  group_by(tank) %>%
  dplyr::select("tank","drilled","wet_weight") %>%
  left_join(musselrespo %>%
              dplyr::select(c("tank", "pH", "temp_treatment")), by = c("tank")) # add treatment data

drilledmodelfull <- glm(drilled ~ pH * temp_treatment, family = "binomial", data = predation_d)
summary(drilledmodelfull)
anova(drilledmodel, test = "Chisq")

drilledmodeltemp <- glm(drilled ~ temp_treatment, family = "binomial", data = predation_d)
summary(drilledmodeltemp)
anova(drilledmodeltemp, test = "Chisq")


predation_d$drill_prob <- predict(drilledmodel, type = "response")
#drillplot <- 
  ggplot(predation_d, aes(x = pH, y = drill_prob, color = temp_treatment, fill = temp_treatment)) +
  geom_point(alpha = 0.4) +
  geom_smooth(method = "loess", se = FALSE) +
  scale_color_manual(values = c("#0072B2", "#D55E00")) +
  labs(x = expression(pH[T]),
       y = "Predicted Probability of Being Drilled", 
       color = expression(paste("Temperature ",degree,"C")), 
       fill  = expression(paste("Temperature ",degree,"C"))) +
  theme_bw()
  
#get rid of pH
predation_d %>% 
  ggplot(aes(x = temp_treatment, y = drill_prob)) +
  geom_boxplot(alpha=0.5, outlier.alpha=0) + 
  geom_jitter(aes(fill = as.numeric(pH)),width=0.25, pch=21, size=2) +
  scale_fill_gradient(low = "palegreen2", high = "#0072B2")+
  theme_bw()+
  theme(
    strip.background = element_rect(fill = "white"),
    text = element_text(size = 14)
  ) +
    labs(x = expression(pH[T]),
       y = "Predicted Probability of Being Drilled", 
       color = expression(paste("Temperature ",degree,"C")), 
       fill  = expression(paste("Temperature ",degree,"C")))
```

### patchworked graphs

```{r}
Mrespoplot + Mcalcplot + plot_layout(guides = "collect", axes = "collect_x")

ggsave("mytilus.png", path=here("Output"), width = 16, height = 8)

Nrespoplot + Ncalcplot + shellgrowthplot + plot_layout(guides = "collect", axes = "collect_x")

ggsave("nucella.png", path=here("Output"), width = 16, height = 8)

eatenplot + drillplot + plot_layout(guides = "collect", axes = "collect_x")

ggsave("nucella predation.png", path=here("Output"), width = 16, height = 8)

```
